FancyMc Moves \\ Fusion Moves for Multicut Objectives

### 2014-09-26 paper/alg_graph.tex
fixed figure

\begin{tikzpicture}
    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]

    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
    \begin{scope}[x={(image.south east)},y={(image.north west)}]
        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
        \draw node[pixel ](100.5,100.5) {BLAAA};
    \end{scope}
\end{tikzpicture}

>>>>

%\begin{tikzpicture}
%    \tikzstyle{pixel}=[regular polygon,regular polygon sides=4,inner sep=0pt,draw,solid,font=\sffamily\small]
%
%    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
%    \begin{scope}[x={(image.south east)},y={(image.north west)}]
%        \draw[red,ultra thick,rounded corners] (0.62,0.65) rectangle (0.78,0.75);
%        \draw node[pixel ](100.5,100.5) {BLAAA};
%    \end{scope}
%\end{tikzpicture}

% 481 / 321
\begin{tikzpicture}[scale=1.0]

    \node[anchor=south west,inner sep=0] (image) at (0,0) 
        {\includegraphics[width=.25\textwidth]{images/120093.jpg}};
    \begin{scope}[x={(image.south east)},y={(image.north west)},xscale=100/481,yscale=100/321]   
        %   \draw (0,0) grid (481,321);
        \draw[gray,xstep=3.21/15, ystep=3.21/15] (0,0) grid (4.81,3.21);
    \end{scope}

\end{tikzpicture}
